\documentclass[12pt]{article}
\usepackage[margin=1.2in]{geometry} 
\usepackage{titling}
\usepackage{pgfgantt}

\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}

\setlength{\droptitle}{-10em}
\title{Project Proposal : Undergraduate Research}
\subtitle{Hierarchical Management of Multi-Agent Teams}
\author{Hugo Garrido-Lestache, CS}
\date{\today}

\begin{document}

\maketitle

This a proposal of my project for Undergraduate Research in MSOE.
This proposal gives a rough idea of what I hope to acomplish.

\section{Goals}
The main goal of this project is to get a deeper understading of reinforcement learning and how to use it effectively.
Subgoals of this project is to create an exceptional reinforcement learning project which stands out on a resume.
Additionally I want to create something novel and publish some research on the topic.

\section{Motivation}
I chose to do this project due to my interest in many reinforcement learning project that I have seen in the past and on the internet.
I also know that I do not have much experience in this area of the field and wanted to expand my knowledge to this part of the field.

\section{Topic}
This topic of this paper is too see how reinforcement agents interact with each other in multi-agent teams.
I want to directly compare the difference between using a seperate agent which can influence the other agents creating this Hierarchy.
The idea is that this coach will act as a leader/manager of the agents creating stronger collaborations than otherwise.

I also want to experiment with different reinforcement learning algorithms to see which one is the most effective in this scenario.
And what combination of algorithms is the most effective.

I am also intrested in implemnting the use "StarCraft II: A New Challenge for Reinforcement Learning" papers ideas create a more robust agent.

\section{Enviroment}
For the choice of Enviroment I wanted to chose a fairly simple enviroment to start with.
I chose the idea of Footbal/Soccer as the enviroment where two teams of agents will play against each other attempting to move a single ball into two set of oposing goals.
The number of agents on each team will could be something to experiment where I see that the effect of Hierarchical Management being more effective on bigger teams.


\section{(super rough) Timeline}

\begin{itemize}
    \item Week 1 - 4 : Research \& Building enviroment.
    \item Week 5 - 8 : Integrating and Implmenting basic Reinforcement Learning Algorithm.
    \item Week 9 - 12 : Implementing Hierarchical Management and Experiment with different algorithms.
    \item Week 13 - 16 : Implementing StarCraft II ideas and develop progress reports.
    \item Week 16 - 20 : Continue to experiment with different parameters and algorithms and record main results.
    \item Week 21 - 30 : Finalize paper, presentation and reprodcution of results.
\end{itemize}


\end{document}